Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-04 paper/galsize_paper.tex
Added a few in-draft comments in blue text

@@

Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical. We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows histograms of stellar mass for the two subsamples. The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} shows a histogram of the stellar masses, confirming that our method yields identical stellar mass functions for the two subsamples. The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
}
\label{fig:sizedefinition}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

>>>>

{\color{blue} AVK comment: Need to be much clearer and more explicit about which galaxy properties come from which dataset, and probably to reiterate this when discussing the Figure \ref{fig:scatter_plot} plot of the size-mass relation.}

@@

Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical. We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows histograms of stellar mass for the two subsamples. The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample. {\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} shows a histogram of the stellar masses, confirming that our method yields identical stellar mass functions for the two subsamples. The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample. {\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}
}
\label{fig:sizedefinition}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all. APH: The big picture being compared/tested here are ``pre-infall" vs. ``post-infall" processes, respectively. Those don't seem like great names either though.}
